Project Description -- Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

\item Additionally effects, such as sedimentation, transport, and compaction constantly work to reconfigure the medium as its constituents and boundaries degrade.
\end{itemize}
These challenges require innovative computational techniques, some of which have been developed recently~\cite{Quaife2018} and others that await resolution. {\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.} Dynamic erosion of porous media is a highly active area of research, as closely related laboratory experiments on erosion in colloidal systems are already being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}. These experiments a great opportunity for comparison against our numerical simulations. Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute (see Section~\ref{sec:experiments}), which would help to guide, calibrate, and validate the computations (see letter of collaboration).

>>>>

\item Additionally effects, such as sedimentation, transport, and compaction constantly work to reconfigure the medium as its constituents and boundaries degrade.
\end{itemize}
These challenges require innovative computational techniques, some of which have been developed recently~\cite{Quaife2018} and others that await resolution. {\bf An ultimate goal of this proposal is to achieve high-fidelity simulations of $\boldsymbol{\mathcal{O}(100-1000)}$ mobile bodies undergoing simultaneous erosion, transport, sedimentation, and compaction, with the computational efficiency required to run large ensembles for statistical analysis.}

	There has been a recent spark in interest in dynamic erosion of porous media, both theoretically and experimentally. In fact, experiments on erosion of colloidal systems are currently being explored in the Datta Lab at Princeton~\cite{bizmark2019multiscale}. These experiments are closely related to our proposed computational study, thus offering a great opportunity for comparison. Furthermore, we propose performing a set of experiments conducted at the nearby the Geophysical Fluid Dynamics Institute (see Section~\ref{sec:experiments}), which would help to guide, calibrate, and validate the computations (see letter of collaboration).
